\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-03 paper/ms.tex
RJObject writing

The specific prior for $N$ was
\begin{align}
p(N) \propto \frac{1}{N+1}
\end{align}
for $N \in \{1, 2, ..., 100\}$.
For the conditional prior of the gaussian parameters,
we used Laplace (biexponential)
distributions\footnote{A Laplace
distribution with location parameter $a$ and scale parameter
$b$ has density $p(x | a, b) = \frac{1}{2}\exp\left(-\frac{1}{b}|x - a|\right)$.}

>>>>

To help with implementing the member functions for the \code{MyModel} class,
the \code{gaussians} object can be generated from its prior, proposed,
and printed trivially as follows:
\begin{CodeInput}
\begin{CodeChunk}
    // Generate the components from the prior
    gaussians.from_prior(rng);

    // Do a Metropolis proposal
    double logH = gaussians.perturb(rng);

    // Print to output stream 'out'
    gaussians.print(out);
\end{CodeChunk}
\end{CodeInput}

The specific prior for $N$ was
\begin{align}
p(N) \propto \frac{1}{N+1}
\end{align}
for $N \in \{1, 2, ..., 100\}$.
For the conditional prior of the gaussian parameters,
we used Laplace (biexponential)
distributions\footnote{A Laplace
distribution with location parameter $a$ and scale parameter
$b$ has density $p(x | a, b) = \frac{1}{2}\exp\left(-\frac{1}{b}|x - a|\right)$.}.
Normal distributions would be more convenional, but the analytic cumulative
distribution function (CDF) of the Laplace distribution makes it easier to
implement.
